An Efficient Interpolation Technique for Jump Proposals in Reversible-Jump Markov Chain Monte Carlo Calculations

### 2011-03-17 paper.tex
Added conclusion.

\section{Conclusion/Discussion}
\label{sec:conclusion}

>>>>

\section{Conclusion}
\label{sec:conclusion}

The need to compare evidences for multiple models arises in a large variety of physical and astronomical contexts.  In this paper, we described a new technique that allows for efficient evidence computations via a Reversible-Jump Markov chain Monte Carlo.  This technique solves the usual problem of finding good inter-model jump proposals in an RJMCMC by using a kD-tree to quickly and accurately interpolate an approximate posterior PDF from a single-model MCMC run, and then using this interpolated PDF to propose efficient inter-model jumps.

We demonstrated the efficiency of this technique on a toy model-comparison problem described in Section \ref{sec:efficiency}.  We also successfully applied this technique to the problem of selecting the best model for the observed distribution of black-hole X-ray binaries, as described in Section \ref{sec:examples} and Ref.~\cite{Farr2010}.   In addition to model comparison, the PDF interpolation described here can be useful in multi-step MCMCs to improve the sampling efficiency by selecting better jump proposal distributions or to test MCMC convergence.

We have made our implementation of the technique described in this paper publicly available online at \will{URL}, and welcome readers to take advantage of this toolkit.

\section*{Acknowledgments}

We are grateful to Neil Cornish for interesting discussions.  IM acknowledges support from the NSF Astronomy and Astrophysics Postdoctoral Fellowship, award AST-0901985.  WF acknowledges support from \will{Add your acknowledgements}
